Think deep for reef resilience

### 2025-08-16 paper/paper_draft.qmd
attempt cleanup of reef carbonate budget

>>>>

## Reef carbonate budget

Reef median depth has a moderate positive correlation with the number of years a reef
maintains coral cover above the assumed carbonate budget threshold required to sustain live
coral cover ($\theta_{0}$). Greater median depth is a key characteristic defining reefs that
sustain coral cover above $\theta_{0}$ [@fig-access-esm1-5-depth-carbonate]. Unsurprisingly,
the number of years above $\theta_0$ substantially decreases as $\theta_0$ is increased, as
does the Spearman's correlation. This is likely due to an increasing number of reefs being
unable to maintain coral cover above $\theta_0$ as the assumed threshold is increased, with
values **\[TI: Ben, could you clarify which values? Coral cover or years above
threshold?\]** becoming increasingly right-skewed. In contrast, log10-transformed total
connectivity strength ($\text{log10}(S)$) was found to have no correlation with the number
of years a reef maintains cover above the required thresholds
[@sfig-access-esm1-5-conn-carbonate] **\[TI: Ben, because we are comparing depth and
connectivity, this figure needs to be shown in the main text\]**. The correlation between
$\text{log10}(S)$ and $\theta_0$ slightly decreases as the assumed threshold for $\theta_0$
increases.
